Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-23 def_fidel_echo.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

\begin{figure}[h]
\centering
\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
\caption{Loschmidt echo of connecting two CFTs. The two infinitely extended sides represent the groundstate of the disconnected chain Hamiltonians. They sandwich the evolution operator at the center, with the Hamiltonian being that of the connected chains. In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (they all represent `DN' in this case). See the discussion in main text.}
\label{fig:echo}
\end{figure}
\todo[inline]{Tianci: Change the single slit to double slit at the LHS, and add $\tau$ at the RHS?}
If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
\end{equation}

The tip of the slit is no longer a twist field with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing(bcc) operator. These diagrams then become the one or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
\caption{Loschmidt echo of connecting two CFTs. The two infinitely extended sides represent the groundstate of the disconnected chain Hamiltonians. They sandwich the evolution operator at the center, with the Hamiltonian being that of the connected chains. In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (they all represent `DN' in this case). See the discussion in main text.}
\label{fig:echo}
\end{figure}
\todo[inline]{Mao: double slits on the LHS, tau on the RHS, please confirm.}

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
\end{equation}

The tip of the slit is no longer a twist field with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing (bcc) operator. These diagrams then become the one or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

### 2017-05-23 disc.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

In all the computation we have done, the fidelity results can be converted to that of the Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$. The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips. Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces. Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will be mainly discuss the echo properties.

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 )
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the echo is always $\frac{1}{4} \ln t$, regardless of the theta angle. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two corresponds to the parts of the Lorentz group and can't be connected by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result with transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

% x dependence, DN -> ND agrees with existing result;
More interesting case is when the boundary conditions are of the same type, which we verified the quadratic angle dependence numerically for the process 
\begin{equation}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} 
\end{equation}
which gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Unfortunately, our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation. This is very likely due to the ambiguity of the free boson zero mode, as moving slight away from the point remedy the situation. And numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, does change the scaling dimensional in a way that is not captured by our analytic computation. Generally speaking, the boundary condition on the far end may introduce additional bcc operator and thus change the free energy. It would be interesting to have a CFT calculation to reproduce the better numerical result of
\begin{equation}
{\rm ND} + {\rm DN} \rightarrow \lambda + {\rm ND} 
\end{equation}

\todo[inline]{insert the ND + DN figure. Compare it with the DN + DN figure}

Nevertheless the special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this and the $DD \rightarrow {\rm P}$ one  $\frac{3}{8}- \frac{1}{4} = \frac{1}{16} $ is interpreted as the bcc operator dimension between D and N. The picture is complete in this full ${\rm DN}$ to $\lambda $ transition.

@@

Aside from free lattice boson model for the numerical purposes, these set of boundary conditions can be realized in connecting two compact bosons. There are already numerous theoretical and experimental work on the boundary conditions of Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides. A X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible.

>>>>

In all the computation we have done, the fidelity results can be converted to that of the Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$. The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips. Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces. Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will mainly discuss the echo properties.

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 )
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can't be connected even by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

% x dependence, DN -> ND agrees with existing result;
More interesting case is when the boundary conditions are of the same type, which we verified the quadratic angle dependence numerically for the process 
\begin{equation}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
\end{equation}
The process gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used). This is very likely due to the ambiguity of the free boson zero mode, as moving slight away from the point remedy the situation. The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one $\frac{1}{4}$ is interpreted as the bcc operator dimension $\frac{1}{16}$ between D and N. This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$. In a rational boson theory, the possible number of primary fields are finite. It requires further study to identify these bcc operators and explore their physical significance.

Numerical study also shows that the outer boundary condition, which in the large system size limit should not impact the system, {\it does change} the scaling dimensional in a way that is not captured by our analytic computation. Generally speaking, the boundary condition on the far end may introduce additional bcc operator and thus change the free energy. It would be interesting to have a CFT calculation to reproduce the better numerical result of
\begin{equation}
{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
\end{equation}
shown in Fig.~\ref{fig:PDN_fit}.

@@

These set of boundary conditions can be realized in connecting two compact bosons. There are already numerous theoretical and experimental work on the boundary conditions of Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides. An X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.

### 2017-05-23 free_boson_lattice.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow
[draft] App. G checked. PDN data added. Whole paper 1st pass.

We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ on lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
\begin{equation}
\label{eq:lattice_H}
H = \frac{1}{2} \sum_i \left(\pi_i^2  + ( \phi_i - \phi_{i+1} )^2 \right) +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
\Sigma
\begin{pmatrix}
\phi_0 \\
\phi_1 
\end{pmatrix}
\end{equation}
%\begin{eqnarray}\begin{aligned}
%H = \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2  +  \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
%\begin{bmatrix}
%1 + \Sigma_{11}  & \Sigma_{12} \\
%\Sigma_{21} &  1 + \Sigma_{22} \\
%\end{bmatrix}
%\begin{pmatrix}
%\phi_0 \\
%\phi_1 
%\end{pmatrix}
%\end{aligned}\end{eqnarray}
where the $2\times2$ matrix $\Sigma$ parameterizes two-site interaction. In fact $\Sigma$ gives a simple relation with the scattering matrix defined in Sec.~\ref{sec_sub:general_formulation}, and thus the Hamiltonian is the lattice regularization of the bosonic interface discussed there. We perform the standard scattering analysis in App.~\ref{app:interface_free_boson}, and the scale invariant S-matrix reads
\begin{equation}
S = \frac{1}{1 - e^{-2ika } } ( -2i \sin ka ) \Sigma
 = - e^{ika} \Sigma
\end{equation}
where $a$ is the lattice constant. In the continuum limit $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
\begin{equation}
\label{eq:def_Sigma}
\Sigma = -\lim_{a \rightarrow 0 } S = 
\begin{bmatrix}
\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
\end{bmatrix}
\end{equation}
where $\lambda\in\mathbb{R}$. The lattice model in Eq.~\eqref{eq:lattice_H} with interface defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results.

>>>>

We consider two harmonic chains with bosonic field $\phi_i$ and conjugate momentum $\pi_i$ on lattice site $i$. The left and right chains are connected between site $0$ and $1$ with the Hamiltonian
\begin{equation}
\begin{aligned}
\label{eq:lattice_H}
H &= \frac{1}{2} \sum_i \pi_i^2  +  \frac{1}{2} \sum_{i\ne 0 }  ( \phi_i - \phi_{i+1} )^2 \\
& + \frac{1}{2} \begin{pmatrix}  \phi_0, \phi_1 \end{pmatrix}
\begin{bmatrix}
1 + \Sigma_{11}  & \Sigma_{12} \\
\Sigma_{21} &  1 + \Sigma_{22} \\
\end{bmatrix}
\begin{pmatrix}
\phi_0 \\
\phi_1 
\end{pmatrix}
\end{aligned}
\end{equation}
where the $2\times2$ matrix $\Sigma$ parameterizes the two-site interaction. We performed the standard scattering analysis in App.~\ref{app:interface_free_boson}. For mode with momentum $k$, the only possible scale invariant S-matrix is
\begin{equation}
S = - e^{ika} \Sigma
\end{equation}
where $a$ is the lattice constant. In the continuum limit $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
\begin{equation}
\label{eq:def_Sigma}
\Sigma = -\lim_{a \rightarrow 0 } S = 
\begin{bmatrix}
\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
\end{bmatrix}
\end{equation}
where $\lambda\in\mathbb{R}$.

The lattice model in Eq.~\eqref{eq:lattice_H} with interface defined in Eq.~\eqref{eq:def_Sigma} will be used to check our analytic results for both Loschmidt echo and fidelity.

### 2017-05-23 general_formulation.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous. An equivalent way of viewing it (and will be used later) is to fold one of the theories on top of the other. The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends here. This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}. In the Boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.

@@

The physical significance of $\theta$ will be manifest in the scattering process described below. We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane. It is then one of the scattering products that leaves the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix}\quad
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. The fact of their wavelength independence is an indication of scale invariance of the interface.

@@

If we quantize the Boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{equation}
\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^n - \bar{a}_{-n } \bar{z}^{-n}   \right)
\end{equation}
where take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ 2\pi ( i\tau - x ) / T } \quad \bar{z} = e^{ -2\pi ( i\tau + x ) / T }
\end{equation}
We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\cos\theta a_n^1-\sin\theta a_n^2 &= +( \cos\theta\bar{a}_{-n}^1-\sin\theta \bar{a}_{-n}^2 ) \\
\sin\theta a_n^1+\cos\theta a_n^2 &= -( \sin\theta\bar{a}_{-n}^1+\cos\theta \bar{a}_{-n}^2 ) 
\end{aligned}
\end{equation}
which is valid on the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous. Eq.~\eqref{eq:bd_state} will be used extensively in the boundary state calculation of fidelity and Loschmidt echo in Sec.~\ref{sec:analytic_numerics}.

>>>>

The general constraint we can impose on an interface is that the momentum flow (or current flow if exists) should be continuous. An equivalent way of viewing it (and will be used later) is to fold one of the theories on top of the other. The interface now located on the boundary of the tensor theory becomes impenetrable, and momentum flow ends there. This folding picture leads to the concept of boundary states in the framework of boundary CFT\cite{cardy_boundary_2004,cardy_conformal_1984}. In the Boson theory we are interested in, the tensor theory has $c = 2$ and the general classification the boundary state is still an open questions\cite{affleck_quantum_2001}.

@@

The physical significance of $\theta$ will be manifest in the scattering process described below. We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane. It is then one of the scattering products that leaves the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix}\quad
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. The fact of their wavelength independence is an indication of scale invariance of the interface.

@@

If we quantize the Boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{equation}
\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^{-n} + \bar{a}_{n} \bar{z}^{-n}   \right)
\end{equation}
where we take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ 2\pi i(x - t) / T } \quad \bar{z} = e^{ 2\pi i( x + t  ) / T }
\end{equation}
We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\cos\theta a_n^1-\sin\theta a_n^2 &= +( \cos\theta\bar{a}_{-n}^1-\sin\theta \bar{a}_{-n}^2 ) \\
\sin\theta a_n^1+\cos\theta a_n^2 &= -( \sin\theta\bar{a}_{-n}^1+\cos\theta \bar{a}_{-n}^2 ) 
\end{aligned}
\end{equation}
which is valid on the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous.

The boundary state expression in Eq.~\eqref{eq:bd_state} will be used extensively in fidelity and Loschmidt echo calculation in Sec.~\ref{sec:analytic_numerics}.

### 2017-05-23 intro.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of physical boundary and isolated impurity weakly break the conformal symmetry. Simply put, they scatter and hence relate the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions exhibit different critical exponent from the bulk\cite{cardy_conformal_1984}. One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problems of this kind that have been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) cross the system. As shown in Fig.~\ref{fig:cut-and-join}, one first prepares the ground states of the critical chain A and B, and then connects them at $t = 0$ and evolves. Various quantities are used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. And the authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution. In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with the boundary critical exponent.

@@

% All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}. The separating ground stats prepared before $t = 0$ are joined to form a new type of interface between them. Before the quench, the slit represents boundaries that are completely reflective to the injecting particles. The joining turns on the transmission from one side to the other. In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of Ref.~\onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.

It would therefore be interesting to connect two different CFTs in the ``cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}. There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study entanglement properties. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the compact Boson case, it is controlled by the ratio of the compactification radii and in the free lattice Boson case by ratio of masses. We expect it to be tunable in a realistic experimental setting.

@@

In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable interface and its lattice realization.

@@

In App.~\ref{app:F_correction}, we point out two corrections to the free energy, namely boundary logarithmic term and Schwarzian term. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation is presented in App.~\ref{app:comp_fid_echo}. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We calculate the free energy of one particular setup as an example in App.~\ref{app:gnd_dn_lambda}. The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}. Throughout this paper, we work exclusively with the oscillator modes of free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} have contribution to the free energy at the leading order. Therefore the results presented in this paper remain valid in the more general case where two compactified bosons of different radii are connected by a conformal interface.

>>>>

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the system's conformal symmetry. Simply put, the scattering on the interface relates the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing (bcc) operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions can exhibit different critical exponent from the bulk counterpart\cite{cardy_conformal_1984}. One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) across the system. As shown in Fig.~\ref{fig:cut-and-join}, we first prepare the system at the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve. Various quantities are used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. The authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution. In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with its boundary critical exponent.

@@

% All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}. The separating ground states prepared before $t = 0$ are joined to form a new type of interface between them. Before the quench, the slit represents boundaries that are completely reflective to the injecting particles. The joining turns on the transmission from one side to the other. In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of Ref.~\onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.

It would therefore be interesting to connect two different CFTs in the ``cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}. There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study their entanglement properties. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the compact Boson case, it is controlled by the ratio of the compactification radii and in the free lattice Boson case by ratio of masses. We expect it to be tunable in a realistic experimental setting.

@@

In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization.

@@

This paper includes several appendices for technical details. In App.~\ref{app:F_correction}, we point out two corrections to the free energy, complementary to the argument made in the main text. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation is presented in App.~\ref{app:comp_fid_echo}. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We calculate the free energy of one particular setup as an example in App.~\ref{app:gnd_dn_lambda}. The result is generalized to arbitrary boundary conditions in App.~\ref{app:lambda_12}. Up until this point, we work exclusively with the oscillator modes of free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order. Therefore the results remain valid in the physical situation of connecting two compactified bosons of different radii.
